\begin{abstract}
India faces a severe shortage of healthcare specialists, particularly in ENT and dermatology. As of March 2023, over 23,000 sanctioned medical posts remained vacant across the country, with more than 9,000 vacancies in primary health centers (PHCs) alone. According to the National Health Profile 2019, India has only about 1 doctor per 1,457 people, far below the WHO recommendation of 1:1,000. The shortage is even more acute in rural areas, where approximately 70\% of India's population resides. Only about 12,000 in India for a population of 1.4 billion are ENT specialists (~1:116,000 ratio) Approximately 11,000 for 1.4 billion people are dermatologists (~1:127,000 ratio). Over 60\% of India's specialists practice in urban areas serving only 30\% of the population.
Approximately 70\% of India's population resides in rural areas, where the shortage of specialists is particularly acute. Rural patients travel long distances to access basic diagnostic services, and the average out-of-pocket cost of a single specialist consultation (including travel) can be over INR 2000-3000. Travel also means loss of daily wage and the impact is on already economically vulnerable sections of the population. Studies show that the delay in diagnosis on account of barriers to access yield more serious complications at the time of the diagnosis, resulting in higher treatment costs.
To mitigate the effects of this, we propose a smart telemedicine system that supports dermatoscopic, pharyngoscopic, and otoscopic viewing using a portable system made up of a camera and microcontroller, which is primarily used for imaging. All images captured by the device can be uploaded by a mobile application and the complete report is generated from AI generated diagnostic reports. Our needs are for remote areas with low access to healthcare – we want to bring primary care providers enhanced capability to diagnose areas of healthcare, in ways that do not have the level of design and infrastructure requirements of many existing solutions or designs.

\end{abstract}
