\begin{thebibliography}{}

% Literature Review

\bibitem{field}
~Field, M. J. (1996). Introduction and background. Telemedicine - NCBI Bookshelf. https://www.ncbi.nlm.nih.gov/books/NBK45440/
\bibitem{who}
~Dasgupta, A., \& Deb, S. (2008). Telemedicine: A new horizon in public health in India. Indian Journal of Community Medicine, 33(1), 3. https://doi.org/10.4103/0970-0218.39234
\bibitem{anto}
~Antoniuk, A. (2025, May 6). AI in Telemedicine: Challenges, Use Cases \& Implementation - TATEEDA | GLOBAL. TATEEDA | GLOBAL - Full cycle custom software development services and outsourcing in the USA and Ukraine. https://tateeda.com/blog/ai-in-telemedicine-use-cases. Retrieved on 12-05-2025, 17:46 IST (GMT +5:30)
\bibitem{leeway}
~Takyar, A. (2023, December 15). AI in telemedicine. LeewayHertz - AI Development Company. https://www.leewayhertz.com/ai-in-telemedicine/
\bibitem{tele}
~Mudur, G. (2024, September 10). 23,000 sanctioned medical posts vacant: Report flags rural-urban government doctor shortage. The Telegraph. https://www.telegraphindia.com/india/report-flags-rural-urban-government-doctor-shortage-23000-sanctioned-medical-posts-vacant/cid/2046918. Retrieved on 12-05-2025, 17:46 IST (GMT +5:30)
\bibitem{pib}
~Update on ratio of patients and doctors nurses. (n.d.). https://www.pib.gov.in/PressReleasePage.aspx?PRID=1985423
\bibitem{ndtv}
Press Trust of India. (2024, February 9). Doctor-Population ratio in country at 1:834, better than WHO standards: Health Minister. www.ndtv.com. https://www.ndtv.com/india-news/doctor-population-ratio-in-country-at-1-834-better-than-who-standards-health-minister-5025731. Retrieved on 12-05-2025, 17:46 IST (GMT +5:30)
\bibitem{swarno}
Swarno. (2025, March 8). Patient-to-Doctor ratio: a real challenge in maintaining quality healthcare. JMN Medical College. https://jmnmedicalcollege.org.in/patient-to-doctor-ratio-a-real-challenge-in-maintaining-quality-healthcare/ Retrieved on 12-05-2025, 17:46 IST (GMT +5:30)
\bibitem{dutta}
Dutta, S. S.(2025, March 3). Rural India has an 80\% shortfall of specialist doctors. MP, Gujarat, Tamil Nadu worst off. ThePrint. https://theprint.in/health/rural-india-has-an-80-shortfall-of-specialist-doctors-mp-gujarat-tamil-nadu-worst-off/2259874/ Retrieved on 12-05-2025, 17:46 IST (GMT +5:30)
\bibitem{bw}
National Doctor’s Day: Severe shortage of specialist doctors, rural areas most affected - BW Healthcare World. (n.d.). BW Health. https://www.bwhealthcareworld.com/article/national-doctor\%E2\%80\%99s-day-severe-shortage-of-specialist-doctors-rural-areas-most-affected-482599. Retrieved on 12-05-2025, 17:46 IST (GMT +5:30)

%Section: Dermatoscopy

\bibitem{oxio}
openoximetry.org/. (2024, September 13). Skin color quantification - OpenOximetry. OpenOximetry. https://openoximetry.org/skin-color-quantification/
\bibitem{book}
Schanda, J. (2007). Colorimetry: Understanding the CIE System. John Wiley \& Sons.
\bibitem{chardon}
Chardon, A., Cretois, I., \& Hourseau, C. (1991). Skin colour typology and suntanning pathways. International Journal of Cosmetic Science, 13(4), 191–208. https://doi.org/10.1111/j.1467-2494.1991.tb00561.x
\bibitem{kinnie}
Kinyanjui, N.M., Odonga, T., Cintas, C., Codella, N.C., Panda, R., Sattigeri, P., Varshney, K.R.: Fairness of classifiers across skin tones in dermatology. In: Medical Image Computing and Computer-Assisted Intervention. pp. 320–329 (2020)
\bibitem{isic2018}
Codella, N., Rotemberg, V., Tschandl, P., Celebi, M.E., Dusza, S., Gutman, D., Helba, B., Kalloo, A., Liopyris, K., Marchetti, M., et al.: Skin lesion analysis toward melanoma detection 2018: A challenge hosted by the international skin imaging collaboration (ISIC). arXiv preprint arXiv:1902.03368 (2019) 2, 13
\bibitem{sun}
Sun, X., Yang, J., Sun, M., Wang, K.: A benchmark for automatic visual classification of clinical skin disease images. In: European Conference on Computer Vision. pp. 206–222. Springer (2016)
\bibitem{groh}
Groh, M., Harris, C., Soenksen, L., Lau, F., Han, R., Kim, A., Koochek, A., Badri, O.: Evaluating deep neural networks trained on clinical images in dermatology with the Fitzpatrick 17k dataset. In: Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition. pp. 1820–1828 (2021) 



% Section: Pharyngoscopy

\bibitem{onto}
~Ontosight.Ai. (n.d.). Pharyngoscopy | Pharyngoscopy medical procedure overview. Ontosight.ai. https://ontosight.ai/glossary/term/pharyngoscopy-medical-procedure-overview--679d730638099fda3cfbca36 Retrieved on 12-05-2025, 17:46 IST \(GMT +5:30\)
\bibitem{kollara}
~Kollara, L., Perry, J. L., \& Hudson, S. (2015). Racial variations in velopharyngeal and craniometric morphology in Children: an imaging study. Journal of Speech Language and Hearing Research, 59(1), 27–38. https://doi.org/10.1044/2015\_jslhr-s-14-0236
\bibitem{choi}
~Choi, J. S., Yin, V., Wu, F., Bhatt, N. K., O’Dell, K., \& Johns, M. (2021). Utility of Telemedicine for Diagnosis and Management of Laryngology‐Related Complaints during COVID‐19. The Laryngoscope, 132(4), 831–837. https://doi.org/10.1002/lary.29838
\bibitem{selva}
Selvaraju, R. R., Cogswell, M., Das, A., Vedantam, R., Parikh, D., \& Batra, D. (2019). Grad-CAM: Visual Explanations from Deep Networks via Gradient-Based Localization. International Journal of Computer Vision, 128(2), 336–359. https://doi.org/10.1007/s11263-019-01228-7
\bibitem{nakajo}
~Nakajo, K., Ninomiya, Y., Kondo, H., Takeshita, N., Uchida, E., Aoyama, N., Inaba, A., Ikematsu, H., Shinozaki, T., Matsuura, K., Hayashi, R., Akimoto, T., \& Yano, T. (2023). Anatomical classification of pharyngeal and laryngeal endoscopic images using artificial intelligence. Head \& Neck, 45(6), 1549–1557. https://doi.org/10.1002/hed.27370

%Section: otoscopy

\bibitem{habibi}
~A meta-analysis and systematic review of AI models for otoscopic image classification showed considerable diagnostic performance across different algorithmic strategies. Technical methods compared were convolutional neural networks (CNNs), artificial neural networks, support vector machines, decision trees, and k-nearest neighbors algorithms. The models were trained to differentiate among several diagnostic classes, namely normal tympanic membrane, acute otitis media, otitis media with effusion, chronic otitis media with/without perforation, cholesteatoma, and ear canal obstruction.

\end{thebibliography}
